2 Party State Assertion Channels

### 2019-01-14 paper/main.tex
Added tests for measuring gas costs and refactored the channel contract to reduce costs of the assertState

	\maketitle
	\begin{abstract}
	%State channels are a scaling technique for cryptocurrencies as it lets a group of parties execute a smart contract locally amongst themselves instead of the global network. 
	%In the best case, the application is no longer restricted by the underlying blockchain's latency and all execution is free as it remains local between the parties. 
	%If there is a disagreement about the latest state of the smart contact, then any party can trigger a dispute which appoints the blockchain as an arbitrator to resolve it. 
	An empirical case study to evaluate state channels as a scaling solution for cryptocurrencies demonstrated that providing an application's full state during the dispute process for a state channel is financially costly (i.e. \$1.5 to \$57.57 for a battleship game) which can hamper their real-world use. 
	To overcome this issue, we present \emph{State Assertion Channels}, the first state channel to guarantee  an honest party is always refunded the cost if it becomes necessary to send an application's full state during the dispute process. 
	Furthermore it ensures an honest party will pay an approximate fixed cost to continue an application's execution via the dispute process. 
	We provide a proof of concept implementation which demonstrates it costs approximately \$x to submit evidence  regardless of the smart contract's application.

@@

%\paragraph{Proof of concept implementation} 
%Table 1 outlines the gas costs for creating the state channel smart contract and its dispute process. 
%As we can see creating the smart contract costs x, and the entire dispute process for a single state assertion costs x. 
%

@@

\paragraph{Bond Requirement} 
Each party must deposit a bond to cover the cost of a successful challenge to their assertion. 
The bond's value must consider the worst-case when a transaction fee spikes due to network congestion. 
For example, in the battleship empirical case study it was highlighted that submitting the game's state can sky rocket from \$1.56 to approximately \$57 during network congestion.  
If the security bond isn't sufficient to challenge a state assertion, then the the counterparty may not challenge it.

\paragraph{Offline parties and PISA} 
There are two issues for a watching service like PISA \cite{mccorry2018pisa} to protect the channel. 
First, an attacker can trigger a dispute with the latest agreed state hash, and then assert an invaid state hash that benefits the attacker.
A watching service must have a copy of the latest state in plaintext to verify the invalid state transition and issue a challenge, but this hinders state privacy.
Second, an attacker can issue a new state assertion and claim all coins after the deadline using $\chanblue.\timeoutblue()$. 
To prevent a timeout, the offline party must delegate the authority to continue the application's execution to the watching service.
Future work should consider whether the execution of an application can be delegated to a third party in an accountable manner

>>>>

	\maketitle
	\begin{abstract}
	%State channels are a scaling technique for cryptocurrencies as it lets a group of parties execute a smart contract locally amongst themselves instead of the global network. 
	%In the best case, the application is no longer restricted by the underlying blockchain's latency and all execution is free as it remains local between the parties. 
	%If there is a disagreement about the latest state of the smart contact, then any party can trigger a dispute which appoints the blockchain as an arbitrator to resolve it. 
	An empirical case study to evaluate state channels as a scaling solution for cryptocurrencies demonstrated that providing an application's full state during the dispute process for a state channel is financially costly (i.e. \$1.5 to \$57.57 for a battleship game) which can hamper their real-world use. 
	To overcome this issue, we present \emph{State Assertion Channels}, the first state channel to guarantee  an honest party is always refunded the cost if it becomes necessary to send an application's full state during the dispute process. 
	Furthermore it ensures an honest party will pay an approximate fixed cost to continue an application's execution via the dispute process. 
	We provide a proof of concept implementation which demonstrates it costs approximately \$0.02 to submit evidence  regardless of the smart contract's application.

@@

\paragraph{Proof of concept implementation} 
Our proof on concept implementation took 2,943,664 gas to deploy. Which  is approximately \$0.97 using the gas price of 2.6 Gwei and the conversion rate of 1 ether = \$127, the real world rate in January 2019. The cost to make a state assertion is 59,774+39.5n gas (\$0.02), where \textit{n} corresponds to the number of bytes supplied as $\inputs$ to the assertion.

@@

\paragraph{Bond Requirement} 
Each party must deposit a bond to cover the cost of a successful challenge to their assertion. 
The bond's value must consider the worst-case when a transaction fee spikes due to network congestion. 
For example, in the battleship empirical case study it was highlighted that submitting the game's state can sky rocket from \$1.56 to approximately \$57 during network congestion.  
If the security bond isn't sufficient to challenge a state assertion, then the counterparty may not challenge it.

\paragraph{Offline parties and PISA} 
There are two issues for a watching service like PISA \cite{mccorry2018pisa} to protect the channel. 
First, an attacker can trigger a dispute with the latest agreed state hash, and then assert an invaid state hash that benefits the attacker.
A watching service must have a copy of the latest state in plaintext to verify the invalid state transition and issue a challenge, but this hinders state privacy.
Second, an attacker can issue a new state assertion and claim all coins after the deadline using $\chanblue.\timeoutblue()$. 
To prevent a timeout, the offline party must delegate the authority to continue the application's execution to the watching service.
Future work should consider whether the execution of an application can be delegated to a third party in an accountable manner.
